---
title: "Solution 21"
output:
  html_document: default
  word_document:
    highlight: monochrome
---


###Problem 21:
The following code uses the for() looping function to plot graphs that compare the relative population growth (here, by the use of a logarithmic scale) for the Australian states and territories.
```
oldpar <- par(mfrow=c(2,4))
for (i in 2:9){
plot(austpop[, 1], log(austpop[, i]), xlab="Year",
ylab=names(austpop)[i], pch=16, ylim=c(0,10))}
par(oldpar)
```

```{r prob21.importScript}
# Read R script for problem 21 into current R Notebook file.
knitr::read_chunk("pdf_prob21.R")
```

```{r prob21.info}
```

```{r prob21.setup}
```

```{r prob21.loadData}
```

Run the for loop.
```{r prob21.runLoop}
```

Find a way to do this without looping. [Hint: Use the function sapply(), with austpop[,2:9] as the first.

We first define the function plotCol1Colx( ) ...
```{r prob21.funcDef}
```

and use it in sapply( )
```{r prob21.funcSapply}
```


Clear the global environment.
```{r prob21.clearEnv}
```